Appendix

### 2015-05-06 Rmarkdown/appendix.Rmd
Update R packages list

```{r R_packages, echo = FALSE, eval = TRUE, message = FALSE, results = "asis"}
library(xtable)
x <- read.table("../data/r_packages.txt",  header = TRUE,
                stringsAsFactors = FALSE, sep = "\t")
# Drop packages with "*" column set, which indicates the package is a
# "dependency of a dependency".
x <- x[x[, 2] != "*", ]
x <- x[, -c(2, 4)]
# Drop MethylationTuples and methsim which are reported elsewhere
x <- x[!x$package %in% c("methsim", "MethylationTuples", "GenomicTUples"), ]
xt <- xtable(x, caption = c("R packages used in thesis as reported by \\texttt{devtools::session\\_info()}", "R packages used in thesis"),
             label = "tab:R_packages")
align(xt) <- rep("l", 4)
print(xt, booktabs = TRUE, comment = FALSE, tabular.environment = "longtable",
      floating = FALSE, include.rownames = FALSE, caption.placement = "top")
```

>>>>

```{r R_packages, echo = FALSE, eval = TRUE, message = FALSE, results = "asis"}
library(xtable)
x <- read.table("../data/r_packages.txt",  header = TRUE,
                stringsAsFactors = FALSE, sep = "\t")
# Drop packages with "*" column set, which indicates the package is a
# "dependency of a dependency".
x <- x[x[, 2] != "*", ]
x <- x[, -c(2, 4)]
# Drop MethylationTuples and methsim which are reported elsewhere
x <- x[!x$package %in% c("methsim", "MethylationTuples", "GenomicTUples"), ]
xt <- xtable(x, caption = c("R packages used in thesis (as reported by \\texttt{devtools::session\\_info()})", "R packages used in thesis"),
             label = "tab:R_packages")
align(xt) <- rep("l", 4)
print(xt, booktabs = TRUE, comment = FALSE, tabular.environment = "longtable",
      floating = FALSE, include.rownames = FALSE, caption.placement = "top")
```
